\thispagestyle{empty}
\vspace*{1.0cm}

\begin{center}
    \textbf{Abstract}
\end{center}

\vspace*{0.5cm}

\noindent
The advancement in technology demand development of advanced tools. The manufacturing of these tools may involve laser manufacturing and phase change. This project is dedicated to the programming of laser-induced melting processes and the tracking of interface positions. There are two approaches programmed in this project. 
The first is the Enthalpy Problem approach, commonly known as fixed grid method and the second one is the Stefan Problem approach commonly known as the front tracking method. Both the methods present significant challenge. The Enthalpy approach is implemented for materials with sharp melting point, as well as materials that undergo melting over a range of temperatures. The Stefan problem is programmed only for materials that melt at a sharp melting point. We work with non-dimensionalized variables, and the techniques used for achieving this are explained in detail within this report. We utilize the Newton-Raphson-Scheme (NRS) to solve the set of non linear equations. Moreover, we employ the Euler implicit time integration scheme in the Enthalpy Problem and Euler forward or explicit time integration scheme for the Stefan Problem to track the position of the interface. In the Enthalpy Problem we aim to capture the sudden jumps in the Enthalpy that arises at the phase change. We have carried out necessary tests and validations to evaluate the results obtained.